Kit Theory

### 2023-06-21 paper/paper.tex
Update.

>>>>

  \subsection{Structure}
  The rest of this paper will introduce our framework using System F
  as a running example for a type soundness proof.

  Code of the framework is displayed in gray boxes.
  Code of examples is written in yellow boxes.
  Code of the System F formalization is written without boxes. This is
  the only code a user of our framework has to write.

  In the paper we state all definitions and lemmas, but omit some proofs
  in the interest of space. However the omitted proofs exclusively
  depend on lemmas and definitions stated in this paper. The full code
  from the paper can be found at TODO.

  In the paper we only show the part of the framework necessary for
  the System F soundness proof. The actual implementation is more
  general and complete and can be found at TODO.
